Bismillahirrahmanirrahim iSLAM\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-02-28 paper/main.tex
Update main.tex

Stereo matching and depth estimation are pivotal in applications such as autonomous driving and robotic navigation. Traditional methods, as outlined by Scharstein and Szeliski (2002), have evolved with the adoption of Deep Neural Network (DNN) techniques, significantly enhancing accuracy (Zbontar & LeCun, 2016). However, the computational demands of these DNN solutions often outpace the capabilities of onboard systems in real-time scenarios (Shamsafar et al., 2022; Rahim et al., 2021).

@@

\section{Technical Approach}
\subsection{Pre-Processing}
\subsubsection{Data Augmentation}
\subsubsection{Stereo Infill}
\subsubsection{Lidar Null Mask}
\subsection{PG: Papoulis GerchBerg}
\subsubsection{PG Background}
\subsubsection{our Approach}
\subsubsection{Use of Band Reject Filter in PG}
\subsubsection{Evaluated PG for Our Work}
\subsection{Post-Proc}
\subsubsection{Removal of Trivial Aumented Data}

@@

\subsubsection{Sensor Suit}
\subsubsubsection{Upsampling of lidar data} %% Further improvements dynamic lidar upsampling with kalman

@@

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

Stereo matching and depth estimation are pivotal in applications such as autonomous driving and robotic navigation. Traditional methods, as outlined by Scharstein and Szeliski (2002), have evolved with the adoption of Deep Neural Network (DNN) techniques, significantly enhancing accuracy (Zbontar \& LeCun, 2016). However, the computational demands of these DNN solutions often outpace the capabilities of onboard systems in real-time scenarios (Shamsafar et al., 2022; Rahim et al., 2021).

@@

\section{Technical Approach}
%% In this section explain the each step of the processing detaily.

Our approach is based on the PG method that is commonly used for kayıplı sinyal kestirimi in communications systems. The method is applicable for 1D signals, originally. The 2D implementation of it is required for us. There are some works on implementation to 2D of PG.

An application of this algorithm is used for image inpainting by \cite{pg-image-inpaint-2009}. They introduce the PG for this specific scenerio but it has some precautions to use for us. The images they used are extremely dense when comparing with the Lidar. Also, they have single sensory image but we need to optain a fusion.

Another work done by \cite{ozbay2015high} that introduce an extended version of PG for 3D point cloud data that is driven by a Lidar sensor. They use this as an upsampling to cope with delayed points when using Lidar in high resolution mode due to the low scan rates of cylindirical scanning ones. But appearantly, it also use single sensory system

We introduce our novel approach my putting another extension of PG to the litarature that is the first one uses multi-sensory system. The nature of PG consists some elements.

%% PG açıklaması başta olsa daha iyi olabilir.

\subsection{Pre-Processing}
\subsubsection{Data Augmentation}
Due to the fundamental difference in the representation of depth information between liDAR measurements (point cloud) and stereo depth estimation (dense disparity maps), both data modalities necessitate preprocessing steps involving transformation, conversion, and upsampling to facilitate their integration and subsequent processing.

REVISE - To make these two sensor data processable in a domain, we determine a common modality for these images. This modality is single channel depth image format. The RGB integration wont necessite for using our algorithm.

\paragraph{Obtaining Depth Frame From Lidar Data}

After making the calibrations for stereo camera and the Lidar, we know all the transformation matrices to generate the depth image from point cloud data. To project the 3D points into the 2D depth frame space we use the intrinsic parameters and the known transformation matrices.

\paragraph{Lidar Null Mask}

\paragraph{Stereo Infill}

\subsection{PG: Papoulis GerchBerg}
%% \subsubsection{PG Background}
%% Cite other papers about papoulis gerchberg, super resolution

\subsubsection{Our Approach}
\subsubsection{Use of Band Reject Filter in PG}
\subsubsection{Evaluated PG for Our Work}
\subsection{Post-Proc}
\subsubsection{Removal of Trivial Aumented Data}

@@

\subsubsection{Sensor Suit}
\paragraph{Upsampling of Lidar Data}
%% Further improvements dynamic lidar upsampling with kalman

@@

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}

\bibliographystyle{plain} % We choose the "plain" reference style
\bibliography{refs} % Entries are in the refs.bib file

\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.
